Individual heterogeneity in the functional topography of the DMN in medial prefrontal cortex 

### 2019-02-05 Manuscript.Rmd
up to results section 2

A potential downfall of our approach lies in whether the considerable computational demands are indeed required to identify these individualized partitions. It is possible that careful seed-based functional connectivity could provide sufficiently stable approximations of an individual's DMN arrangement. Given the high variability and idiosyncrasy of mPFC (see Results), we examined if SP could capture more reliable maps than seed-based functional connectivity in this area. First, we estimated each subject's DMN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average PCC activity for each day separately. We compared these seed-based maps with the Fiedler vectors produced by SP by spatially correlating them across days and subjects in three ways: 1) between seed-based maps; 2) between community-based maps; and 3) between correlation- and community-based maps. These spatial correlations were aimed to determine the day-to-day stability of each approach, as well as the overall level of agreement between them. These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Mueller2013a]). We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).

@@

We performed a coordinate-based meta-analysis to identify unique standard regions across DMN and SV literatures (see Methods). Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study. The 25 areas considered were limited to the medial portion of the DMN, as defined by Yeo et al.[-@Yeo2011]. Unique areas were identified by permuting the affiliation of each study (i.e. DMN or SV) to create a null distribution of chi-squared statistics, which was used to identify regions more often reported in either literature. Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.

>>>>

A potential downfall of our approach lies in whether the considerable computational demands are indeed required to identify these individualized partitions. It is possible that regional seed-based functional connectivity could provide sufficiently stable approximations of an individual's DMN arrangement. Given the high variability and idiosyncrasy of mPFC (see Results), we examined if SP could capture more reliable maps than seed-based functional connectivity in this area. First, we estimated each subject's DMN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average PCC activity for each day separately. We compared these seed-based maps with the Fiedler vectors produced by SP by spatially correlating them across days and subjects in three ways: 1) between seed-based maps; 2) between community-based maps; and 3) between correlation- and community-based maps. These spatial correlations were aimed to determine the day-to-day stability of each approach, as well as the overall level of agreement between them. These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Mueller2013a]). We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).

@@

We performed a coordinate-based meta-analysis to identify unique standard regions across DMN and SV literatures. Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study. The 25 areas considered were limited to the medial portion of the DMN, as defined by Yeo et al.[-@Yeo2011]. Unique areas were identified by first permuting the affiliation of each study (i.e. DMN or SV) to create a distribution of Chi-squared statistics based on the comparison of the number of reports per area between literatures (see Methods for details). This putative null distribution was used to identify regions more often reported in either literature. Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.
